---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 
```{r}
library(MCexposure)
require(ggplot2)
require(lattice)
require(GGally)
require(reshape2)
require(raster)
 
require(gridExtra)
require(ggthemes)
require(cowplot)
require(ggpubr)
require(rasterVis)
```

Reproduce method comparison scatterplot figure using scatter_compare_method
```{r, fig.show='hold'}

data(homemaker)
data(commuter)
data(location)
data(AP_5m)
rl = list(homemaker,commuter,AP_5m); 
scatter_compare_methods(rl, location)

```

reproduce transect figure using plottransec (middle and bottom figure), drawtrasectline(upper figure)
```{r plottranset}


 
tra_we= rbind(c(120000,456000), c(145000, 456000))
tra_ns= rbind(c(135000,450000), c(135000, 470000))
WEho=plottransec(homemaker, tra_we, tra_NS = tra_ns, "west-east")
NSho = plottransec(homemaker, tra_we, tra_NS =tra_ns , "north-south")
WEco = plottransec(commuter, tra_we, tra_NS = tra_ns, "west-east")
NSco = plottransec(commuter, tra_we, tra_NS =tra_ns , "north-south")
ho  = drawtransectline(homemaker, tra_we, tra_NS = tra_ns)
co = drawtransectline(commuter, tra_we, tra_NS = tra_ns)
tra_g= arrangeGrob(ho,co, WEho,NSho, WEco, NSco,  ncol = 4, nrow = 3, 
             layout_matrix = rbind(c(1,2), c(1,2), c(3,5), c(3,5), c(4,6), c(4,6))) 
  as_ggplot(tra_g)+draw_plot_label(label = c("Commuter","west-east transect ", "north-south transect","Homemaker","west-east transect ", "north-south transect"), size = 18,
                  x = c(0.6, 0.55, 0.55,0.15, 0.09, 0.09 ), y = c( 0.98, 0.68, 0.33,0.98, 0.68, 0.33))
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
